12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2017-06-19 rules/rules17.tex
Allow declare-datatype(s) commands if the logic features algebraic datatypes
Extend deadline to 2017-06-19

\begin{description}
\item[May~1] Deadline for new benchmark contributions.
\item[June~1] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~4] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~18] Deadline for final versions of solvers, including
  system descriptions.
\item[June~19] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~22/23] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.6, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there may be a single
    \akey{set-option :print-success ...} command.  Note that
    \texttt{success} outputs are ignored by the post-processor used by
    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
      a \texttt{success} answer after each \akey{set-logic},
      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
      command (among others), unless the option \akey{:print-success}
      is set to false.  Ignoring the \texttt{success} outputs allows
      for submitting fully SMT-LIB~2.6 compliant solvers without the
      need for a wrapper script, while still allowing entrants of
      previous competitions to run without changes.}
  \item In the application track, the \akey{:print-success} option
    must not be disabled.  The trace executor will send an initial
    \akey{set-option :print-success true} command to the solver.
  \end{enumerate}
\item In the unsat-core track, there is a single \akey{set-option
  :produce-unsat-cores true} command.
\item The (single) \akey{set-logic} command setting the benchmark's
  logic is the first command after any \akey{set-option} commands.
\item The script may contain any number of \akey{set-info} commands.
\item The script may contain any number of \akey{declare-sort} and
  \akey{define-sort} commands.  All sorts declared or defined with
  these commands must have zero arity.
\item The script may contain any number of \akey{declare-fun} and
  \akey{define-fun} commands.
\item The script may contain any number of \akey{assert} commands.
  All formulas in the script belong to the benchmark's logic, with any
  free symbols declared in the script.
\item
  \begin{enumerate}
    \item In the main and application track, named formulas are not
      used.
    \item In the unsat core track, top-level assertions may be named.
  \end{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there is exactly one
    \akey{check-sat} command.
  \item In the application track, there are one or more
    \akey{check-sat} commands.  There may also be zero or more
    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
    consistent with the use of those commands in the SMT-LIB standard.
  \end{enumerate}
\item In the unsat-core track, the \akey{check-sat} command (which is
  always issued in an unsatisfiable context) is followed by a single
  \akey{get-unsat-core} command.
\item The script may optionally contain an \akey{exit} command as its
  last command.  In the application track, this command must not be
  omitted.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

>>>>

\begin{description}
\item[May~1] Deadline for new benchmark contributions.
\item[June~1] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~4] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[June~19] Deadline for final versions of solvers, including
  system descriptions.
\item[June~20] Opening value of NYSE Composite Index used to complete
  random seed for benchmark scrambling.
\item[July~22/23] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.6, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there may be a single
    \akey{set-option :print-success ...} command.  Note that
    \texttt{success} outputs are ignored by the post-processor used by
    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
      a \texttt{success} answer after each \akey{set-logic},
      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
      command (among others), unless the option \akey{:print-success}
      is set to false.  Ignoring the \texttt{success} outputs allows
      for submitting fully SMT-LIB~2.6 compliant solvers without the
      need for a wrapper script, while still allowing entrants of
      previous competitions to run without changes.}
  \item In the application track, the \akey{:print-success} option
    must not be disabled.  The trace executor will send an initial
    \akey{set-option :print-success true} command to the solver.
  \end{enumerate}
\item In the unsat-core track, there is a single \akey{set-option
  :produce-unsat-cores true} command.
\item The (single) \akey{set-logic} command setting the benchmark's
  logic is the first command after any \akey{set-option} commands.
\item The script may contain any number of \akey{set-info} commands.
\item The script may contain any number of \akey{declare-sort} and
  \akey{define-sort} commands.  All sorts declared or defined with
  these commands must have zero arity.
\item The script may contain any number of \akey{declare-fun} and
  \akey{define-fun} commands.
\item If the benchmark's logic features algebraic datatypes, the
  script may contain any number of \akey{declare-datatype(s)}
  commands.
\item The script may contain any number of \akey{assert} commands.
  All formulas in the script belong to the benchmark's logic, with any
  free symbols declared in the script.
\item
  \begin{enumerate}
    \item In the main and application track, named formulas are not
      used.
    \item In the unsat core track, top-level assertions may be named.
  \end{enumerate}
\item
  \begin{enumerate}
  \item In the main and unsat-core track, there is exactly one
    \akey{check-sat} command.
  \item In the application track, there are one or more
    \akey{check-sat} commands.  There may also be zero or more
    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
    consistent with the use of those commands in the SMT-LIB standard.
  \end{enumerate}
\item In the unsat-core track, the \akey{check-sat} command (which is
  always issued in an unsatisfiable context) is followed by a single
  \akey{get-unsat-core} command.
\item The script may optionally contain an \akey{exit} command as its
  last command.  In the application track, this command must not be
  omitted.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.
